The Unintended Consequences of Energy Reduction

### 2024-02-14 paper/paper.qmd
Added abstract and removed unecessary code

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
library(palmerpenguins)
```

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

@@

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

>>>>

---
title: "The Unintended Consequences of Energy Reduction"
subtitle: "How an Act of Environmental Protection Led to the Deaths of Many"
author:
  - Yi Fei Pang
  - Irene Hyunh
  - Tara Chakkithara
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Nuclear energy is a clean power source that produces electricity while operating with low-carbon emissions. Although nuclear power generation has its advantages, many concerns have been raised regarding its safety after the Fukushima nuclear accident of 2011. This paper analyzes the utilization of nuclear energy, the price of electricity and electricity consumption, and the temperature-mortality relationship in Japan before and after the accident. We reveal that the use of nuclear energy in Japan sharply decreased following the nuclear accident, resulting in a power shortage and surge in electricity prices across Japan. This prompted the country’s government to push an energy saving mindset to the public, and as a result, electricity consumption plummeted. However, we find that the government’s efforts created adverse effects as days with high temperatures coupled with an energy saving mindset led to a higher mortality rate. These findings prompt discussions about the true cost of energy saving."
pdf-engine: pdflatex
format:
  pdf:
    documentclass: article
    geometry:
      - top=30mm
      - left=20mm
      - heightrounded
include: false
warning: false
message: false
number-sections: true
bibliography: references.bib
---

@@

library(tidyverse)
```

@@

@@

@@

@@

@@
